Blocking-resistant communication\\through domain fronting

### 2014-11-23 docs/meek.tex
Some rewriting.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy.
The \meek\ server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server, which is presumed blocked by the censor.
The server receives HTTP requests, decodes them, and feeds their payloads into a Tor relay,
returning downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including
[blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

Hiding the endpoint and obscuring byte patterns are important parts of blocking-resistant communication,
but there are other, more subtle considerations.
We describe what we have done to disguise other traffic ``tells'' in \meek,
such as using a real web browser as a tool for making fronted HTTPS requests,
in order to disguise meek's TLS fingerprint.
We argue that these measures, combined with domain fronting, increase the censor's effort
beyond simple one-shot blocking techniques such as IP address blocking, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}

>>>>

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy
that decodes a sequence of HTTP requests and feeds their contents into Tor.
A censor sees only a sequence of HTTPS requests to an allowed domain.
We describe our experience with deploying \meek.
% \meek, or something based on it,
% has been adopted by other circumvention systems including
% [blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

Hiding the endpoint and obscuring byte patterns are important parts of blockinging resistance,
but there are other, more subtle considerations.
We describe what we have done to disguise traffic ``tells'' in \meek,
including using a real web browser to make fronted HTTPS requests
in order to disguise the TLS fingerprint.
We argue that these measures, combined with domain fronting, increase the censor's effort
beyond simple one-shot blocking techniques such as IP address blacklisting, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}
